Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-18 ms/S2_appendix.tex
very small comment and tweaks to supp file

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_1.pdf}
\caption{{\bf Envelopes of transmission trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of population-mean transmission probabilities rather than expected progression time to AIDS over time
for each model.
}
\label{fig:transtraj}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of SPVL trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of \Lspvl\ rather than expected progression time to AIDS over time
for each model.
}
\label{fig:virtraj}
\end{figure}

@@

%% \Lspvl\ doesn't get bolded so I got rid of log10
\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and SPVL.}
This figure matches Fig 3 in main text, but displays the
univariate distributions for the transmission probability and \Lspvl\ time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of progression time to AIDS.
}
\label{fig:tranvirsum}
\end{figure}

@@

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_4.pdf}
\caption{{\bf Effects of contact heterogeneity and vital dynamics.}
This figure matches Fig 3 in main text, but displays the
summary statistics of the modified explicit models (models with contact heterogeneity and vital dynamics).
For each model, its summary statistics are plotted on the univariate plot using different shapes.
All models were simulated using the baseline parameters.
}
\label{fig:fig3aug}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_1.pdf}
\caption{{\bf Envelopes of transmission trajectories under all models.}
This figure matches Fig 3 in main text, but displays the
envelope of population-mean transmission probabilities rather than mean \Lspvl\ over time
for each model.
}
\label{fig:transtraj}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of expected progression time to AIDS trajectories under all models.}
This figure matches Fig 3 in main text, but displays the
envelope of expected progression time to AIDS rather than mean \Lspvl\ over time
for each model.
}
\label{fig:durtraj}
\end{figure}

@@

%% \Lspvl\ doesn't get bolded so I got rid of log10
\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and expected progression time to AIDS.}
This figure matches Fig 4 in main text, but displays the
univariate distributions for the transmission probability and expected progression time to AIDS time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of \Lspvl.
}
\label{fig:trandursum}
\end{figure}

@@

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_4.pdf}
\caption{{\bf Effects of contact heterogeneity and vital dynamics.}
This figure matches Fig 4 in main text, but displays the
summary statistics of the modified explicit models (models with contact heterogeneity and vital dynamics).
For each model, its summary statistics are plotted on the univariate plot using different shapes.
All models were simulated using the baseline parameters.
}
\label{fig:fig3aug}
\end{figure}
